\documentclass[a4paper]{article} 
\usepackage{standalone}
\usepackage{import}
\input{../../../../newpreamble.tex}
\usepackage{fancyhdr}
\pagestyle{fancy}
\title{Stat 215A Homework 1}
\author{Lance Remigio}

\begin{document}
\maketitle   

\lhead{Lance Remigio}
\chead{Homework 1}
\rhead{\thepage}
\begin{prop}[A.1.1]
   For all sets \( A, B , C \subseteq \Omega \). 
   \begin{enumerate}
        \item[(1)] Union and intersection commutative and distributive:
            \begin{enumerate}
                \item[(i)] \( A \cup B   = B \cup A \) 
                \item[(ii)] \( A \cap B = B \cap A  \)
                \item[(iii)] \( (A \cup B) \cup C  = A \cup (B \cup C) \)
                \item[(iv)] \( (A \cap B) \cap C  = A \cap (A \cap C) \)
                \item[(v)] \( A \cap (B \cup C ) = (A \cap B) \cup (A \cap C) \)
                \item[(vi)] \( A \cup (B \cap C) = (A \cup B) \cap (A \cup C) \)
            \end{enumerate}
        \item[(2)] \( (A^{c})^{c} = A  \), \( \emptyset^{c} = \Omega\), and \( \Omega^{c} = \emptyset \);
        \item[(3)] \( \emptyset \subseteq  A  \);
        \item[(4)] \( A \subseteq  A  \);
        \item[(5)] \( A \subseteq  B   \) and \( B \subseteq A  \) implies \( A \subseteq  C  \);
        \item[(6)] \( A \subseteq  B  \) if and only if \( B^{c} \subseteq  A^{c} \);
        \item[(7)] \( A \cup A = A = A \cap A  \);
        \item[(8)] \( A \cup \Omega = \Omega \) and \( A \cap \Omega = A  \);
        \item[(9)] \( A \cup \emptyset = A  \) and \( A \cap \emptyset = \emptyset \).
   \end{enumerate}
\end{prop}

\subsection*{Part (1)}

\begin{enumerate}
    \item[(i)]  \( A \cup B = B \cup A  \)
        \begin{proof}
        Our goal is to show that \( A \cup B = B \cup A  \). It suffices to show the following two containments:
        \[  A \cup B \subseteq  B \cup A \tag{*}  \]
        and
        \[  B \cup A \subseteq  A \cup B. \tag{**} \]
        We will first show (*). Let \( x \in A \cup B  \) be arbitrary. Then either \( x \in A  \), \( x \in B  \), or in both. If \( x \in A  \), then \( x \in B \cup A  \). If \( x \in B  \), then \( x \in B \cup A  \). If \( x  \) is in both \( A  \) and \( B  \), then \( x \in B \cup A  \). Hence, in all three cases, \( x \in B \cup A  \) and so \( A \cup B \subseteq  B \cup A  \), satisfying (*). To show (**), let \( x \in B \cup A  \) be arbitrary. Then either \( x \in B  \), \( x \in A  \), or \( x  \) is in both \( A  \) and \( B  \). If \( x \in B  \), then \( x \in B \cup A  \) by definition. If \( x \in A   \), then \( x \in A \cup  B \). If \( x  \) is in both \( A  \) and \( B  \), then \( x \in A \cup B \). Thus, in all three cases, \( x \in A \cup B \).

        \end{proof}
    \item[(ii)] \( A \cap B = B \cap A  \)
        \begin{proof}
        Our goal is to show that \( A \cap B = B \cap A  \). It suffices to show the following two containments:
        \[ A \cap B \subseteq  B \cap A  \tag{*}  \]
        and
        \[  B \cap A \subseteq  A \cap B. \tag{**}  \]
        To show (*), let \( x \in A \cap B  \) be arbitrary. Then this holds if and only if \( x \in A  \) and \( x \in B \). That is, \( x \in B  \) and \( x \in A  \). Thus, \( x \in B \cap A   \). Hence, \( A \cap B \subseteq B \cap A  \), proving (*). Let \( x \in B \cap A  \) be arbitrary. Then both \( x \in B  \) and \( x \in A  \). Thus, \( x \in A  \) and \( x \in B  \). Therefore, \( x \in A \cap B  \) and so \(  B \cap A \subseteq  A \cap B  \), proving (**). From (*) and (**), we get \( A \cap B = B \cap A \).
        \end{proof}
    \item[(iii)] \( (A \cup B) \cup C = A \cup (B \cup C ) \)
        \begin{proof}
      Our goal is to show that \( A \cup (B \cup C) = (A \cup B) \cup C  \). We will show the following two containments:
        \[  A \cup (B \cup C) \subseteq  (A \cup B) \cup C \tag{*} \]
        and
        \[  (A \cup B) \cup C \subseteq A \cup (B \cup C). \tag{**} \]
        To show (*), let \( x \in A \cup (B \cup C) \) be arbitrary. Then either \( x \in A  \), \( x \in B \cup C  \), or in both. If \( x \in A  \), then \( x \in A \cup B \) since \( A  \) is one of the sets in the union \( A \cup B \). Hence, \( x \in (A \cup B) \cup C  \), by the same reasoning (that is, \( A \cup B  \) is contained in one of the sets in the union \( (A \cup B) \cup C   \)). If \( x \in B \cup C  \), then either \( x \in B  \), \( x \in C  \), or \( x \in B \cap C  \). If \( x \in B  \), then \( x \in A \cup B  \) since \( B  \) is contained in \( A \cup B \). Thus, \( x \in (A \cup B) \cup C  \) since \( A \cup B  \) is contained in \( (A \cup B) \cup C  \). If \( x \in C  \), then \( x \in (A \cup B) \cup C  \) because \( C  \) is contained in \( (A \cup B) \cup C  \). If \( x  \) is in both, then immediately \( x \in (A \cup B) \cup C  \) (since we only need \( x  \) to be in at least one of the sets). Now, if \( x \in A  \) and \( x \in B \cup C  \), then we have \(x \in A  \) and \( x \in B  \) or \( x \in C  \). If \( x \in B  \), then since \( x \in A  \), we have \( x \in A \cup B \). Since \( A \cup B  \) is contained in \( (A \cup B) \cup C  \), we also have \( x \in (A \cup B) \cup C  \). Similarly, if \( x \in C  \), then \( x \in (A \cup B) \cup C  \) because \( C   \) is contained in the union \( (A \cup B) \cup C  \). Thus, we conclude that \( A \cup (B \cup C ) \subseteq (A \cup B) \cup C  \).

        To show (**), let \( x \in (A \cup B) \cup C  \) be arbitrary. Then either \( x \in A \cup B \), \( x \in C  \) or both. If \( x \in A \cup B \), then either \( x \in A    \) or \( x \in B \) or both. If \( x \in A  \), then \( x \in A \cup (B \cup C ) \) since \( A  \) is contained in the union \( A \cup (B \cup C ) \). If \( x \in B \), then \( x \in B \cup C  \) since \( B  \) is contained in the union \( B \cup C  \). Since \( B \cup C  \) is contained in the union \( A \cup (B \cup C )  \), \( x \in A \cup (B \cup C) \). Now, if \( x \in C  \), then \( x \in B \cup C  \). By definition, this tells us that \( x \in A \cup (B \cup C ) \) by the same reasoning as before. If \( x  \) is in both, then we have \( x \in A \cup (B \cup C ) \) (since it is in all of them and we only require \( x  \) to be in one of them at least). Thus, we have \( (A \cup B) \cup C \subseteq A \cup (B \cup C ) \).
        \end{proof}
    
    \item[(iv)] \( (A \cap B) \cap C  = A \cap (B \cap C) \)
        \begin{proof}
        Our goal is to show that \( (A \cap B) \cap C  = A \cap (A \cap C) \). We will show the following two containments:
        \[  (A \cap B) \cap C \subseteq  A \cap (B \cap C) \tag{*} \]
        and
        \[  A \cap (B \cap C) \subseteq  (A \cap B) \cap C.  \tag{**} \]
        To show (*), let \( x \in (A \cap B) \cap C  \) be arbitrary. Then \( x \in A \cap B \) and \( x \in C  \). Thus, \( x \in A  \), \( x \in B  \) and \( x \in C  \). Thus, \( x \in A  \) and \( x \in B \cap C  \). By definition, \( x \in A \cap (B \cap C) \). Thus, \( (A \cap B) \cap C \subseteq A \cap (B \cap C) \), proving (*).

        To show (**), let \( x \in A \cap (B \cap C)  \) be arbitrary. Then \( x \in A  \) and \( x \in B \cap C \). Thus, \( x \in A  \), \( x \in B  \), and \( x \in C  \). Now, \( x \in A \cap B  \) and \( x \in C  \) and so \( x \in (A \cap B) \cap C  \), by definition. Therefore, \( A \cap (B \cap C) \subseteq  (A \cap B) \cap C  \), proving (**). Thus, (*) and (**) implies that \( (A \cap B) \cap C = A \cap (B \cap C) \).
       

        \end{proof}    
    \item[(v)] \( A \cap (B \cup C) = (A \cap B) \cup (A \cup C ) \)
        \begin{proof}
        Our goal is to show that \( A \cap (B \cup C) = (A \cap B) \cup (A \cup C) \). We will show the following two containments:   
        \[  A \cap (B \cup C ) \subseteq  (A \cap B) \cup (A \cap C) \tag{*} \]
        and
        \[  (A \cap B) \cup (A \cap C) \subseteq A \cap (B \cup C). \tag{**} \]
        Starting with (*), let \( x \in A \cap (B \cup C) \) be arbitrary. Then \( x \in A  \) and \( x \in B \cup C \). Since \( x \in B \cup C  \), then either \( x \in B  \) or \( x \in C \) or both. Now, if \( x \in B \), then since \( x \in A  \) as well, we have \( x \in A \cap B \). But now \( x  \) lies in at least one of the sets in the union \( (A \cap B) \cup (A \cap C) \). Hence, \( x \in (A \cap B) \cup (A \cap C) \) and so \( A \cap (B \cup C) \subseteq  (A \cap B) \cup (A \cap C) \). Likewise, if \( x \in C  \), then since \( x \in A  \) as well, we have \( x \in A \cap C  \). By definition of union, \( x \in (A \cap  B) \cup (A \cap C) \). Thus, \( A \cap (B \cup C) \subseteq (A \cap B) \cup (A \cap C)  \). Now, if it is in both then \( x \in B  \) and \( x \in C  \). Hence, \( x \in A  \) implies \( x \in A \cap B  \) and \( x \in A \cap C  \), and so we have \( x \in (A \cap B) \cup (A \cap C) \). Thus, we have   
        \[  A \cap (B \cup C ) \subseteq  (A \cap B) \cup (A \cap C ), \]
        proving (*).

        With (**), let \( x \in (A \cap B) \cup (A \cap C) \). Then either \( x \in A \cap B \) or \( x \in A \cap C  \) or both. If \( x \in A \cap B \), then \( x \in A  \) and \( x \in B  \). Since \( x \in B \), it must lie in \( B \cup C  \) because it is contained in at least one of the sets within that union. Thus, we have \( x \in A  \) and \( x \in B \cup C  \) and so \( x \in A \cap (B \cup C) \). Therefore, \( (A \cap B) \cup (A \cap C) \subseteq A \cap (B \cup C) \). If \( x \in A \cap C \), then \( x \in A  \) and \( x \in C  \). Since \( x \in C  \), it follows that \( x \in B \cup C  \) by the same reasoning as before. So, \( x \in A  \) and \( x \in B \cup C  \). Then \( x \in A \cap (B \cup C) \) and so, \( x \in (A \cap B) \cup (A \cap C) \). Thus, \( (A \cap B) \cup (A \cap C) \subseteq A \cap (B \cup C) \), proving (**).

        From (*) and (**), we have our desired result. 
        \end{proof}
    \item[(vi)] \( A \cup (B \cap C) = (A \cap B) \cup (A \cap C)  \)
        \begin{proof}
        Our goal is to show that \( A \cup (B \cap C) = (A \cup B) \cap (A \cup C) \). It suffices to show the following two containments:
        \[  A \cup  (B \cap C) \subseteq (A \cup B) \cap (B \cup C) \tag{*} \]
        and
        \[  (A \cup B) \cap (B \cup C) \subseteq  A \cup (B \cap C). \tag{**} \]
        Starting with (*), let \( x \in A \cup (B \cap C) \) be arbitrary. Then \( x \in A  \) or \( x \in B \cap C \) or both. If \(x \in A  \), then \( x \in A \cup B \) because \( x  \) is contained in at least one of the sets in \( A \cup B  \) (of course, it is \( A  \)). But we also have that \( x \in A \cup C  \) by the same reasoning. Hence, \( x \in A \cup B  \) and \( x \in A \cup C  \). So, \( x \in (A \cup B) \cap (A \cup C) \) and so \( A \cup (B \cap C) \subseteq (A \cup B) \cap (B \cup C)  \). If \( x \in B \cap C \), then \( x \in B  \) and \( x \in C  \). Since \( x \in B  \), then \( x \in A \cup B  \) since \( B  \) is contained in the union \( A \cup B  \). Since \( x \in C  \), then \( x \in A \cup C  \). Thus, \( x \in (A \cup B) \cap (A \cup C) \) and so 
        \[  A \cup (B \cap C) \subseteq  (A \cup B) \cap (A \cup C). \]
        Now, if \( x \in A  \) and \( x \in B \cap C \). Then \( x \in A  \) and \( x \in B  \) and \( x \in C  \). Since \( x \in A  \) and \( x \in B  \), we have \( x \in A \cup B  \). Since \( x \in A  \) and \( x \in C  \), then \( x \in A \cup C  \). Thus, \( x \in ( A \cup B) \cap (A \cup C ) \) and so 
        \[  A \cup (B \cap C) \subseteq  (A \cup B) \cap (A \cup C ), \]
        thereby proving (*).
 
        With (**), let \( x \in (A \cup B) \cap (B \cup C) \) be arbitrary. Then \( x \in A \cup B \) and \( x \in A \cup C  \). Now, we have \( x \in A  \) or \( x \in B  \) (or both) and \( x \in A  \) or \( x \in C  \) (or both). Then \( x \in A  \) or \( x \in B  \) and \( x \in C  \). Thus, \( x \in A  \) or \( x \in B \cap C  \). Therefore, \( x \in A \cup (B \cap C) \). If \( x \in A \cap B \) and \( x \in A \cap C  \), then \( x \in A  \) and \( x \in B  \) and \( x \in C  \). Thus, \( x \in A  \) and \( x \in B \cap C  \) and so \( x \in A \cap (B \cap C ) \)      
        \end{proof}
\end{enumerate}

\subsection*{Part (3)} Prove that \( \emptyset \subseteq  A  \).

\begin{proof}
        Our goal is to show that \( \emptyset \subseteq  A  \). Let \( x \in \emptyset \) be arbitrary. Clearly, this is false by definition of the empty set \( \emptyset  \) and so \( x \in A  \) is a vacuously true statement. Hence, it follows that \( \emptyset \subseteq  A  \).
    \end{proof}

\subsection*{Part (2)}

\begin{enumerate}
    \item[(i)] \( (A^{c})^{c} = A \)
    \begin{proof}
        Our goal is to show that 
        \[ (A^{c})^{c} \subseteq A \tag{1}  \] and 
        \[ (A^{c})^{c} \supseteq A \tag{2}. \]

        Let \( x \in (A^{c})^{c} \) be arbitrary. Since \( A^{c} = \Omega \setminus  A  \), we have  
        \[  (A^{c})^{c} =  \Omega \setminus  A^{c}. \]
        Hence, \( x \in \Omega \), but \( x \notin A^{c} \). However, \( x \notin A^{c} \) implies that \( x \notin \Omega \) or \( x \in A  \). Note that the former yields a contradiction because \( x \in \Omega  \) from an earlier statement. Thus, it must be the case that \( x \in A \). Hence, \( (A^{c})^{c} \subseteq  A   \).

        For the containment in (2), assume for contradiction that \( A \not\subseteq (A^{c})^{c} \). Hence, there exists an \( x \in A  \) such that \( x \notin (A^{c})^{c} \). By definition of complement with respect to \( \Omega \), we have \( (A^{c})^{c} = \Omega \setminus  A^{c} \). Since \( x \notin (A^{c})^{c} \), then either \( x \notin \Omega \) or \( x \in A^{c}  \). If \( x \notin \Omega \), then we have a contradiction because we assumed that \( x \in A  \) earlier. If \( x \in A^{c} = \Omega \setminus  A  \), then we are also saying that \( x \in \Omega \) but \( x \notin A  \) which contradicts our earlier assumption that \( x \in A  \). Hence, we must have that \( A \subseteq  (A^{c})^{c} \).
    \end{proof}
    \item[(ii)] \( \emptyset^{c} = \Omega \)
    \begin{proof}
    Our goal is to show that \( \emptyset^{c} = \Omega \). We will show the following two containments:
    \[  \emptyset^{c} \subseteq    \Omega \tag{*}  \]
    and
    \[  \Omega \subseteq  \emptyset^{c}. \tag{**} \]
    Starting with (*), let \( x \in \emptyset^{c} \) be arbitrary. Since \( \emptyset \subseteq  \Omega  \), we have \( x \in \Omega \setminus  \emptyset \). Hence, \( x \in \Omega  \) but \( x \notin \emptyset \). Thus, \( \emptyset^{c} \subseteq  \Omega  \), proving (*).
    \end{proof}
    \item[(iii)] \( \Omega^{c} = \emptyset \) \textbf{Come back to this proof}
\begin{proof}
    Note that, by part (3), \( \emptyset \subseteq  \Omega^{c} \). To get the equality, it suffices to show that \( \Omega^{c} \subseteq  \emptyset \). Suppose for contradiction that there exists an \( x \in \Omega^{c} \) such that \( x \notin \emptyset \). Thus, \( x \in \emptyset^{c } = \Omega \) (because we have that \( \emptyset \subseteq  \Omega \)) and so \( x \in \Omega \) which contradicts our assumption that \( x \in \Omega^{c} \). 
\end{proof}
\end{enumerate}

\( A \subseteq B  \implies A^{c} = B \setminus  A \) and so for \( \Omega \subseteq \Omega   \), then \( \Omega^{c} = \Omega \setminus  \Omega \)




\subsection*{Part (4)}  Prove that \( A \subseteq  A  \).

\begin{proof}
    Let \( x \in A  \) be arbitrary. Note that \( x \in A  \) because otherwise \( x \notin A = \Omega \setminus  A  \) which would mean that \( x \in \Omega  \) but \( x \notin A  \) would contradict our assumption that \( x \in A  \). Hence, \( A \subseteq  A  \).
\end{proof}

\subsection*{Part (5)} If \( A \subseteq  B  \) and \( B \subseteq  C  \), then \( A \subseteq  C  \).

\begin{proof}
    Suppose \( A \subseteq  B  \) and \( B \subseteq  C  \). Our goal is to show that \( A \subseteq  C  \); that is, for all \( x \in A  \), \( x \in C  \). To this end, let \( x \in A  \) be arbitrary. Since \( A \subseteq B  \), we have \( x \in B \). Since \( B \subseteq C  \), we have \( x \in C  \). Thus, \( A \subseteq  C  \).
\end{proof}

\subsection*{Part (6)}

\( A \subseteq  B   \) if and only if \( B^{c} \subseteq  A^{c} \).

\begin{proof}
\( (\Longrightarrow) \) Suppose \( A \subseteq  B  \). Our goal is to show that \( B^{c} \subseteq A^{c} \). Suppose for contradiction that \( B^{c} \not\subseteq A^{c} \). Then there exists an \( x \in B^{c} \) such that \( x \notin A^{c}  \). Since \( x \notin A^{c}  \), it follows that \( x \in (A^{c})^{c} \). But from part (2), we have \( (A^{c})^{c} =A  \). Thus, \( x \in A  \). Since \( A \subseteq B \), we have \( x \in B \) which is a contradiction.

\( (\Longleftarrow) \) Suppose \( B^{c} \subseteq  A^{c} \). Our goal is to show that \( A \subseteq B \). Suppose for contradiction that \( A \not\subseteq B \). Then there exists an \( x \in A  \) such that \( x \notin B \). Then \( x \in B^{c} \). But \( B^{c} \subseteq A^{c}  \), and so \( x \in A^{c} \). Thus, \( x \notin A   \) which is a contradiction. Thus, \( A \subseteq B \).  
\end{proof}

\subsection*{Part (7)}

Prove that \( A \cup A = A = A \cap A  \).

\begin{proof}
Our goal is to show that \( A \cup A = A = A \cap A  \). First, we will show that \( A \cup A = A  \). We will show the following containments; \( A \cup A \subseteq A  \) and \( A \subseteq  A \cup A  \). Starting with the first containment, let \( x \in A \cup A  \) be arbitrary. Then \( x \in A  \) or \( x \in A  \) or \( x  \) in both. In either case, \( x \in A  \) and so \( A \cup A \subseteq A  \) because \( A \subseteq  A  \) in part (4). If \( x  \) is in both, then \( x \in A  \) by using the same fact. Hence, \( A \cup A \subseteq  A  \). For the second containment, let \( x \in A  \) be arbitrary. Immediately, \( x \in A  \) or \( x \in A  \) since \( A \subseteq  A  \) and \( x  \) lies in all the sets in the union \( A \cup A  \). Thus, \( x \in A \cup A  \). Hence, \( A \cup A = A  \).   

Second, we will show that \( A \cap A = A  \). Let \( x \in A \cap A  \) be arbitrary. Then \( x \in A  \) and \( x \in A  \). Hence, \( x \in A  \) since \( A \subseteq  A   \) in part (4) and so \( A \cap A \subseteq  A  \). Let \( x \in A  \) be arbitrary. Then immediately \( x \in A  \) and \( x \in A  \) by using part (4) again. Hence, \( x \in A \cap A  \) and so \( A \subseteq A \cap A  \).
\end{proof}

\subsection*{Part (8)}

Prove that \( A \cup \Omega = \Omega \) and \( A \cap \Omega = A   \).

\begin{proof}
Our goal is to show that \( A \cup \Omega = \Omega \) and \( A \cap \Omega = A  \). Starting with the first equation, it suffices to show that 
\[  A \cup \Omega \subseteq \Omega \tag{1} \]
and
\[  \Omega \subseteq A \cup \Omega. \tag{2} \]
For (1), let \( x \in A \cup \Omega \) be arbitrary. Then either \( x \in A  \) or \( x \in \Omega \) or \( x  \) is in both. If \( x \in A  \), we have
\[  A \subseteq \Omega \implies x \in \Omega. \]
Clearly, we see that \( x \not\in \emptyset  \) because both \( A  \) and \( \Omega \) are non-empty sets. 
So, \( A \cup \Omega \subseteq \Omega \). On the other hand, if \( x \in \Omega \), we are done. If \( x  \) is in both, then we have \( x \in \Omega \) and \( x \in A  \). Since \( A \subseteq \Omega \), we have 
\[  A \cup \Omega \subseteq \Omega \cup \Omega = \Omega  \]
by part (4). Thus, \( A \cup \Omega \subseteq  \Omega \). 

For (2), let \( x \in \Omega \) be arbitrary. Since \( \Omega \subseteq \Omega \), it follows that \( x  \) is contained in the union \( A \cup \Omega \) containing \( \Omega \). Hence, \( x \in A \cup \Omega \) and so \( A \subseteq A \cup \Omega \).

Now, we will show \( A \cap \Omega = A  \). We will first show \( A \cap \Omega \subseteq  A  \). Let \( x \in A \cap \Omega \) be arbitrary. Then \( x \in A  \) and \( x \in \Omega \). Since \( x \in A  \), we have \( A \cap \Omega \subseteq  A  \). Let \( x \in A  \) be arbitrary. Since \( A \subseteq  \Omega \), we have \( x \in \Omega \). Since \( x \in A  \) and \( x \in \Omega \), we have \( x \in A \cap \Omega \). Thus, \( A \subseteq  A \cap \Omega \). 
\end{proof}

\subsection*{Part (9)}
Prove that \( A \cup \emptyset = A  \) and \( A \cap \emptyset = \emptyset \).
\begin{proof}
Our goal is to show the following two equations:
\[  A \cup \emptyset = A \tag{1} \]
and 
\[  A \cap \emptyset = \emptyset \tag{2}  \]

First, we show (1). It suffices to show that \[ A \cup \emptyset \subseteq A \tag{*}   \]  
and 
\[ A \subseteq  A \cup \emptyset. \tag{**} \] To show the first containment, we use the fact that \( A \cup A = A  \), \( A \subseteq  A  \) and \( \emptyset \subseteq A  \) to get  
\[  A \cup \emptyset \subseteq  A \cup A  = A.  \]
Hence, the first containment is proved.

To show the second containment, suppose for contradiction that \( A \not\subseteq A \cup \emptyset \). Then there exists an \( x \in A  \) such that \( x \not\in A \cup \emptyset \). Then \( x \in (A \cup \emptyset)^{c} \). That is, \( x \in A^{c} \cap \emptyset^{c} \). But from part (2), \( \emptyset^{c} = \Omega \). Hence, \( x \in A^{c} = \Omega \setminus  A  \), but \( x \in \Omega \). That is, \( x \notin A  \), but \( x \in \Omega \) which contradicts the assumption that \( x \in A  \). Therefore, we must have \( A  \subseteq  A \cup \emptyset  \).  

\end{proof}





\end{document}
